Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) }

### 2021-04-01 paper/related-work.tex
Add contract work

>>>>

Contracts are similar to assume-guarantee reasoning but are targeted to programming languages. Contracts are often more expressive than assume-guarantee reasoning and can not only be stateful but higher-order \cite{10.1145/583852.581484}. As contracts are often written in the target language, synthesis is not a problem for monitoring but comes with significant overhead \cite{10.1007/978-3-642-28869-2_11}. A monitor for a contract can be removed when it can be statically proved that the code preserves the contract under all possible inputs and executions \cite{10.1145/3158139}.
